Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-19 writeup/gz_hubble_data.tex
Small fixes to text; closes #89.

As active galactic nuclei often have bright, unresolved optical emission, AGN
have the potential to mimic or distort the identification of a bulge component.
GZH thus includes a set of images designed to measure the effect of AGN on
morphological classifications.  The presence of an AGN was simulated by
modeling the point spread function (PSF) of the telescope and then inserting a
bright source near the center of a real galaxy. For each image, the simulated
AGN was assigned one of three colors -- either blue, red, or flat (white) as
seen in the color images -- and a range of brightnesses such that
$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
with different simulated AGN for each host, in addition to the original galaxy
image.

@@

The dimming and resolution effects of redshift can significantly affect galaxy
classifications derived from any method. To facilitate corrections due to
redshift, we include a sample of 288 galaxies with at redshifts such that
available SDSS imaging can be transformed to simulate \hst{} imaging out to $z
= 1$. The selection spanned a variety of galaxy morphologies (as selected by
GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned
the redshift range of SDSS targets (in $N_z = 4$ bins) in order to optimize for
different target minimum redshifts in \hst{} imaging. We redshifted the
galaxies and produced simulated \hst{} imaging using the \ferengi{} code
\citep{bar08a}.

>>>>

As active galactic nuclei often have bright, unresolved optical emission, AGN
have the potential to mimic or distort the identification of a bulge component.
GZH thus includes a set of images designed to measure the effect of AGN on
morphological classifications.  The presence of an AGN was simulated by
modeling the point spread function (PSF) of the telescope and then inserting a
bright source near the center of a real galaxy. For each image, the simulated
AGN was assigned one of three colors -- either blue, red, or flat (white) as
seen in the color images -- and a range of brightnesses such that
$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
$(0.2,1.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
with different simulated AGN for each host, in addition to the original galaxy
image.

@@

The dimming and resolution effects of redshift can significantly affect galaxy
classifications derived from any method. To facilitate corrections due to
redshift, we include a sample of 288 galaxies with SDSS imaging that can be
transformed to simulate \hst{} imaging out to $z = 1$. The selection spanned a
variety of galaxy morphologies (as selected by GZ2 classifications) and
$r^\prime$-band surface brightnesses, and also spanned the redshift range of
SDSS targets (in $N_z = 4$ bins) in order to optimize for different target
minimum redshifts in \hst{} imaging. We redshifted the galaxies and produced
simulated \hst{} imaging using the \ferengi{} code \citep{bar08a}.
